### 2016-08-05 notions.tex
cheers

\subsection{Relationships Among Notions}
If we allow for trivial schemes, e.g. $M=S$, then correctness and the stronger version of one-wayness privacy (Priv) are clearly orthogonal.
\tsnote{My $M=S\setminus\{x\}$ for a random $x \in S$ construction is less trivial (it compresses), but also serves to separate correctness from Priv.}
\tsnote{In general, it isn't clear how to reduce
correctness to the Priv notion.  In the correctness experiment, you
  get~$(S,\aux)$ but not~$M$; whereas in the Priv-notion, the
  adversary expects~$(M,\aux)$ as input.  Unless the coins of Rep are
  effectively leaked in~$\aux$, you can't reliably produce~$M$
  given~$(S,\aux)$.} 
Curiously, $M=S$ does seem to be both correct and private (up to the element-wise min-entropy of~$S$) in the weaker version of one-wayness privacy (wPriv).
\tsnote{Reducing correctness to the weaker version, wPriv, is syntactically possible, but not clear how to connect the success events.  In the one-wayness game, you win by outputing an element of~$S$; but how does this lead to finding an error-inducing query?  Maybe the one-wayness attacker makes no queries, and just outputs a point~$z$.  Then the correctness attacker does what?  Ask some query~$q_z$ related to~$z$ ---remember, queries are not syntactically restricted to set membership!--- and see if the oracle returns the true value $q_z(S)$?  This is pretty complicated... and it's not clear how to do a quality reduction.   }

>>>>

\subsection{Relationships Among Notions}

\heading{Privacy notions. }
Clearly we have priv $\Rightarrow$ wpriv, tightly and by a simple
reduction.  We should be able to show
\begin{itemize}
\item ss-rep $\Rightarrow$ ind-qry
\item ind-qry $\Rightarrow$ ss-rep \tsnote{Not sure about this separation...}
\item ind-qry $\Rightarrow$ priv \emph{for set-multiplicity data
    structures} \tsnote{but probably not in general}
\item \{w\}priv $\not\Rightarrow$ ind-qry
\item wpriv $\not\Rightarrow$ priv \tsnote{$M=S$, or my
    $M=S\setminus \{x\}$ for a random $x\in S$, if you want something
    a bit less trivial. I'm sure there are more natural schemes that
    will separate, too.}
\end{itemize}

\heading{Correctness vs.\ Privacy. }
If we allow for trivial schemes, e.g. $M=S$, then correctness and the stronger version of one-wayness privacy (Priv) are clearly orthogonal.
\tsnote{My $M=S\setminus\{x\}$ for a random $x \in S$ construction is less trivial (it compresses), but also serves to separate correctness from Priv.}
\tsnote{In general, it isn't clear how to reduce
correctness to the Priv notion.  In the correctness experiment, you
  get~$(S,\aux)$ but not~$M$; whereas in the Priv-notion, the
  adversary expects~$(M,\aux)$ as input.  Unless the coins of Rep are
  effectively leaked in~$\aux$, you can't reliably produce~$M$
  given~$(S,\aux)$.} 
Curiously, $M=S$ does seem to be both correct and private (up to the element-wise min-entropy of~$S$) in the weaker version of one-wayness privacy (wPriv).
\tsnote{Reducing correctness to the weaker version, wPriv, is syntactically possible, but not clear how to connect the success events.  In the one-wayness game, you win by outputing an element of~$S$; but how does this lead to finding an error-inducing query?  Maybe the one-wayness attacker makes no queries, and just outputs a point~$z$.  Then the correctness attacker does what?  Ask some query~$q_z$ related to~$z$ ---remember, queries are not syntactically restricted to set membership!--- and see if the oracle returns the true value $q_z(S)$?  This is pretty complicated... and it's not clear how to do a quality reduction.   }
